---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

Since [isoreader](http://www.github.com/KopfLab/isoreader) and isoviewer are still going through the vetting process, they are not yet submitted to the Comprehensive R Archive Network (CRAN) you can install them easily from GitHub using the `devtools` package:

```{r gh-installation, eval = FALSE}
install.packages("devtools") # only if you don't have this installed yet
devtools::install_github("KopfLab/isoreader")
devtools::install_github("KopfLab/isoviewer")
```

## Using the User Interface

Once isoviewer is installed, you can easily launch the user interface on your local machine by using the `run` function and providing the path to the directory where your data is stored (the `data_dir` parameter). Additional optional parameters control other aspects of the GUI and can be set as needed. See `?isoviewer::run` for help. To run it as a local server accessible via your network, make sure to specify the correct `host` IP address and a fixed `port` (see `?shiny::runApp` for details).

```{r, eval = FALSE}
library(isoviewer)
run(data_dir = ".")
```

## Online Demo

An online demo of the isoviewer GUI is [available on our server](http://server.kopflab.com/shiny/apps/isoviewer/) but has limited computational resources (i.e. could be slow).

